---
title: "BDIA Testing"
author: "Ryan DuPont"
date: "2022-12-20"
output: html_document
---

```{r setup, include=FALSE}
# Install adobeanayticsr from github
devtools::install()
devtools::install_github('ryanAtSdi/adobeanalyticsr')

# Load the package
library(adobeanalyticsr)
```

# bdia_pageview_template() TESTING

## bdia_pageview_template() is a function that writes a template to the global environment 
## with the minimum required columns to aid users in using BDIA

## 1 - Default
## Expected output: 0x5 dataframe with cols: reportSuiteID, userAgent, timestamp, 
## pageName, marketingCloudVisitorID
```{r}
bdia_pageview_template()
pageview_template
colnames(pageview_template)
```

## 2 - URL as page param
## Expected output: 0x5 dataframe with cols: reportSuiteID, userAgent, timestamp,
## pageURL, marketingCloudVisitorID
```{r}
bdia_pageview_template(pageParam = 'url')
pageview_template
colnames(pageview_template)
```

## 3 - Query string as page param
## Expected output: 0x5 dataframe with cols: reportSuiteID, userAgent, timestamp,
## queryString, marketingCloudVisitorID
```{r}
bdia_pageview_template(pageParam = 'qstring')
pageview_template
colnames(pageview_template)
```

## 4 - Visitor ID as unique identifier
## Expected output: 0x5 dataframe with cols: reportSuiteID, userAgent, timestamp,
## pageName, visitorID
```{r}
bdia_pageview_template(idParam = 'vid')
pageview_template
colnames(pageview_template)
```

## 5 - IP Address as unique identifier
## Expected output: 0x5 dataframe with cols: reportSuiteID, userAgent, timestamp,
## pageName, IPAddress
```{r}
bdia_pageview_template(idParam = 'ip')
pageview_template
colnames(pageview_template)
```

## 6 - Custmer ID as unique identifier
## Expected output: 0x6 dataframe with cols: reportSuiteID, userAgent, timestamp,
## pageName, customerID.test.id, customerID.test.isMCSeed
```{r}
bdia_pageview_template(idParam = 'cid', cidType = 'test')
pageview_template
colnames(pageview_template)
```

## 7 - Custmer ID as unique identifier w/o cidType param
## Expected output: Throw error "Input "cidType" is required when selecting Customer ID 
## as your idParam."
```{r}
bdia_pageview_template(idParam = 'cid')
pageview_template
colnames(pageview_template)
```

# ####
# bdia_df2gz() TESTING

## bdia_df2gz() is a helper function that will write a df to a csv file then zip it in the
## format required for BDIA

## Expeced output: fakeData.csv.gz written to the working directory
```{r}
#create df
bdia_pageview_template()
fake_data <- c(
  'ageo1xxpnwryantest',
  'Not Available',
  '2022-12-19T08:01:30-05:00',
  'BDIATest',
  '99999999999999999999999999999999999999'
)
pageview_template[1,] <- fake_data

#run function
bdia_df2gz(pageview_template, 'fakeData')
```

# ####
# bdia_validate_file() TESTING

## bdia_validate_file() sends a zipped data file to the BDIA validation endpoint. This will 
## let the user know if any required columns are missing.

## 1) Valid file sent
## Expected output: "{\"success\":\"file is valid\"}"
```{r}
#jwt auth
adobeanalyticsr::aw_auth('jwt')

#validate file
bdia_validate_file('fakeData.csv.gz')
```

## 2) Invalid file sent
## Expected output: "{\"error\":\"There must be one of QueryString, PageName, or PageUrl defined in the file header.\\nProcessing complete. No valid rows to submit.\\nNo valid rows were found in the file.\"}"
```{r}
#create new file, missing pageName
library(dplyr)
pv_invalid <- pageview_template %>%
  select(-pageName)

bdia_df2gz(pv_invalid, 'invalidFile')

#send invalid file to validation endpoint
bdia_validate_file('invalidFile.csv.gz')
```

# ####
# bdia_send_events() TESTING

## bdia_send_events() sends a zipped data file to the BDIA events endpoint, which will send
## the data to your report suite. As a backstop, the function will hit the validation endpoint
## first, and only attempt to send to the events endpoint IF the file is validated. 

## 1) Valid file sent, default visitor group
## Expected output: 
## "{\"success\":\"file is valid\"}"
## "{\"file_id\":\"e2bb5e0c-e8f9-490f-a264-31ee9c75a0d6\",\"visitor_group_id\":\"vg0\",\"size\":
## 159,\"received_date\":1671594121,\"rows\":1,\"invalid_rows\":0,\"upload_name\":
## \"fakeData.csv.gz\",\"status\":\"File received, awaiting processing\",
## \"status_code\":\"UPLOADED\",\"processing_log\":\"Processing complete: 1 rows 
## will be submitted.  No invalid rows.
## \\n\",\"idempotency_key\":\"e2bb5e0c-e8f9-490f-a264-31ee9c75a0d6\"}"

## Note: Your output will have different IDs and received date values. 
```{r}
bdia_send_events('fakeData.csv.gz')
```

## 1) Valid file sent, visitor group set to 'testGroup'
## Expected output: 
## "{\"success\":\"file is valid\"}"
## "{\"file_id\":\"e2bb5e0c-e8f9-490f-a264-31ee9c75a0d6\",\"visitor_group_id\":\"testGroup\",
##\"size\": 159,\"received_date\":1671594121,\"rows\":1,\"invalid_rows\":0,\"upload_name\":
## \"fakeData.csv.gz\",\"status\":\"File received, awaiting processing\",
## \"status_code\":\"UPLOADED\",\"processing_log\":\"Processing complete: 1 rows 
## will be submitted.  No invalid rows.
## \\n\",\"idempotency_key\":\"e2bb5e0c-e8f9-490f-a264-31ee9c75a0d6\"}"

## Note: Your output will have different IDs and received date values. 
```{r}
bdia_send_events('fakeData.csv.gz', vgid = 'testGroup')
```

## 3) Invalid file sent
## Expected output: "{\"error\":\"There must be one of QueryString, PageName, or PageUrl defined ## in the file header.\\nProcessing complete. No valid rows to submit.\\nNo valid rows were 
## found in the file.\"}"
## File could not be validated. No request made to the events endpoint.
```{r}
bdia_send_events('invalidFile.csv.gz')
```

